---
title: "03: Applying the dictionary"
author: "Jamie Montgomery"
output: 
  html_document:
    theme: paper
    toc: true
    toc_float: true
    toc_depth: 2
---

This script takes the geotagged twitter data and applies the dictionary to the tweets to identify whether or not each tweet is considered "nature-based".

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(kableExtra)
library(sf)
library(mapview)
```

Load data
```{r, message = FALSE, warning = FALSE}
data       <- read_csv("../data/geotag_sb_tweets_user_type.csv")
dictionary <- read_csv("../data/dictionary.csv")
```

Create a function to apply to each tweet that identifies whether there is a word in it or not. Since all dictionary words are lower case, we also turn the full_text column lowercase.

```{r}
nature_df <- data %>%
  dplyr::mutate(full_text = tolower(full_text)) %>%
  dplyr::mutate(nature_word = ifelse(
    str_detect(full_text, paste(c(dictionary$word),collapse = '|')) == TRUE, 1, 0
  )) 
```

Let's look at some examples

```{r}
kable(sample_n(nature_df %>% filter(nature_word == 1), 20)) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), font_size = 10, fixed_thead = T)
```

# Where are nature-based tweets?

```{r}
nature_sf <- nature_df %>%
  st_as_sf(coords = c("lon", "lat")) %>%
  st_set_crs(4326)

hex_grid <- read_sf("../data/sb_area_hexagons.shp")

hex_tweet_count_nature <- hex_grid %>%
  mutate(tweet_count = lengths(st_intersects(hex_grid, nature_sf %>% filter(nature_word == 1))),
         log_tweet_count = log(tweet_count))

#color palettes
greens = colorRampPalette(c("#E5F5E0", "#00441B"))

m <- mapview(hex_tweet_count_nature %>% filter(tweet_count > 0), 
        zcol = "tweet_count", 
        layer.name = "# Nature tweets",
        col.regions = greens) 

m@map %>% setView(lng = -119.714, lat = 34.426, zoom = 12)
```

There are a LOT of nature-based tweets coming from one point.

```{r}
nature_df %>%
  filter(nature_word == 1) %>%
  group_by(geo_coordinates) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  head()
```

What's being tweeted at c(34.42, -119.7)?
```{r}
n <- nature_df %>%
  filter(nature_word == 1,
         geo_coordinates == "c(34.42, -119.7)")

kable(sample_n(n, 10)) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), font_size = 10, fixed_thead = T)
```

It looks like a weather tweet bot! With the same user id (120332550). This account has `r nrow(filter(data, user_id == 120332550))` tweets in our dataset. It looks like the account is [_SantaBarbaraCA](https://twitter.com/_SantaBarbaraCA).

I'm going to filter this account out of our dataset as it will skew our data.

```{r}
nature_df <- nature_df %>% filter(user_id!=120332550)
write_csv(nature_df, "../data/tweets_nature_categorized.csv")
```


# Who is tweeting nature-based tweets?

Assign four categories so we can better look at how tourists and locals tweet about nature (or not).
```{r}
nature_df_user_type <- nature_df %>%
    mutate(coords = gsub("\\)|c\\(", "", geo_coordinates)) %>%
    separate(coords, c("lat", "lon"), sep = ", ") %>%
    mutate_at(c("lon", "lat"), as.numeric) %>% 
    st_as_sf(coords = c("lon", "lat")) %>%
    st_set_crs("+init=epsg:4326") %>%
  mutate(tweet_type = ifelse(nature_word == 1, "nature tweet", "non-nature tweet"),
         nature_user = case_when(
            user_type == "local" & nature_word == 0 ~ "local, non nature tweet",
            user_type == "tourist" & nature_word == 0 ~ "tourist, non nature tweet",
            user_type == "tourist" & nature_word == 1 ~ "tourist, nature tweet",
            user_type == "local" & nature_word == 1 ~ "local, nature tweet"
        ))
```

Not surprisingly there are less nature-based tweets than non nature-based. Of all `r nrow(nature_df)` tweets, `r nrow(nature_df %>% filter(nature_word == 1))/nrow(data)*100`% are nature-based. 

Of local tweeters, `r nrow(nature_df %>% filter(nature_word == 1, user_type == "local"))/nrow(nature_df %>% filter(user_type == "local"))*100`% of tweets are nature-based. Of tourists, `r nrow(nature_df %>% filter(nature_word == 1, user_type == "tourist"))/nrow(nature_df %>% filter(user_type == "tourist"))*100`% are nature-based.

```{r}
ggplot(nature_df_user_type, aes(x = tweet_type, fill = tweet_type)) +
  geom_bar() +
  theme_classic() +
  labs(y = "# Tweets",
       x = "Type of tweet") +
  theme(legend.position = "none") +
  facet_wrap(~user_type) +
  scale_x_discrete(labels=c("Nature", "Non-nature")) +
  scale_fill_manual(values = c("darkgreen", "darkgray")) 
```

