---
title: "Clean CPAD data"
author: "Jamie Afflerbach"
date: "2/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(mapview)
library(tidyverse)
library(mapedit)
library(sp)
library(sf)
library(leaflet)
```

Load california protected areas database
```{r}
cpad <- read_sf("../data/CPAD_2019a/CPAD_2019a_Holdings.shp") %>%
  filter(COUNTY == "Santa Barbara") %>%
  st_transform("+init=epsg:4326") %>%
  st_crop(xmin = -119.5, xmax = -120.5, ymin = 33.88, ymax = 34.6)
```

Map of CPAD areas in Santa Barbara
```{r}
cpad_map <- mapview(cpad, zcol = "UNIT_NAME", legend = FALSE)
cpad_map@map %>% setView(lng = -119.714, lat = 34.426, zoom = 13)
```

# Fix polygons

Some of these polygons do not fully encompass the actual park or designated area. I use `mapedit` to expand the polygons. I did this for:

- Carpinteria bluffs

```{r mapedit_polygons}
carp <- cpad %>%
  filter(SITE_NAME == "Carpinteria Bluffs Public Open Space")
# 
# carp_fix <- mapview(carp, legend = FALSE) %>%
#   editMap("carp")

carp_done <- carp_fix$finished %>%
  mutate(SITE_NAME = "Carpinteria Bluffs Public Open Space",
         ACCESS_TYP = "Open Access",
         HOLDING_ID = 2187) %>%
  select(-X_leaflet_id, -feature_type)
  
```


There are some issues with how some of these polygons are named. Most apparent is the three polygons with UNIT_NAME "Santa Barbara Maitime Musem". Aside from the typo, this name is assigned to the museum itself as well as the harbor and west beach.

There are multiple polygons with the same site name (e.g. Douglas preserve, elings park, sb harbor). I combine those into one polygon here. I also fix some site names.

```{r fix}
cpad_select <- cpad %>%
  select(HOLDING_ID, ACCESS_TYP, SITE_NAME) %>%
  mutate(SITE_NAME = case_when(
    HOLDING_ID == 1964 ~ "Santa Barbara Harbor",
    HOLDING_ID == 1949 ~ "Santa Barbara Harbor",
    HOLDING_ID == 1698 ~ "Santa Barbara Maritime Museum",
    HOLDING_ID == 3284 ~ "Carrillo Recreation Center",
    SITE_NAME == "El Capitán State Beach" ~ "El Capitan State Beach",
    SITE_NAME == "Elings Park - Elings Park Foundation" ~ "Elings Park",
    SITE_NAME == "Honda Valley Park - Community Environmental Council" ~ "Honda Valley Park",
    HOLDING_ID %in% c(2039,2044) ~ "Blueberry Hill Neighborhood Park", 
    TRUE ~ as.character(SITE_NAME)
      )
    ) %>%
  rbind(carp_done) %>%
  group_by(SITE_NAME) %>%
  summarise() %>%
  ungroup()
```

Apply a small buffer to try and capture tweets nearby but not overlapping. For example if you zoom in on Chase Palm Park, a lot of tweets clearly from the park are not captured in the current polygons.

```{r}
cpad_buffer <- cpad_select %>%
  st_buffer(dist = .0001)
  
```


```{r}
#mapview(cpad_select, zcol = "SITE_NAME", legend = FALSE)
write_sf(cpad_buffer, "../data/cpad_fixed.shp", driver = "ESRI Shapefile")
```